Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2025-02-19 paper/numresults.tex
review of section 2 finished
change symbols and write todo list for results
restructure Chebyshev expansion and adjust notation

>>>>

\color{black}
\textcolor{red}{
To do in this section:
\begin{itemize}
    \item Specify implementation details (no non-negative Chebyshev expansion, speed-up tricks, thresholding, ...)
    \item Clarify where code come from (faithful implementation, own code, ...)
    \item Give experimental setup (software version, hardware, single-threaded, ...)
\end{itemize}
}
